Exploring the Role of Small Molecules in Biological Systems Using Network Approaches

### 2015-03-01 paper.tex
ensure proper figure size
updated author ordering Started on intro section

\title{Exploring the Role of Small Molecules in Biological Systems Using Network Approaches}
\author{Sourav Das and Rajarshi Guha}

@@

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.75\linewidth]{img/sim-network-connected}
  \caption{An example of a similarity network, where nodes are
    molecules and are connected if they exhibit a Tanimoto similarity
    greater than 0.6. Nodes are colored based on the PANTHER
    \cite{Mi:2005qq} class of their primary target.}
  \label{fig:simnet}
\end{figure}

>>>>

\title{Exploring the Role of Small Molecules in Biological Systems Using Network Approaches}
\author{Rajarshi Guha and Saurav Das}

@@

The traditional, reductionist view of biology has considered the
behavior and interactions of individual molecular entities as a way to
understand and explain biological phenomena. This approach has become
embodied in the ``one-target, one-drug''  approach to drug
development. Leaving aside the subtleties of how targets are defined,
it has become apparent that this model does not correspond very well
to reality. Instead, it has become increasingly clear that many drugs
(and more generally, small molecules) interact with multiple targets,
including their putative primary target.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{img/sim-network-connected}
  \caption{An example of a similarity network, where nodes are
    molecules and are connected if they exhibit a Tanimoto similarity
    greater than 0.6. Nodes are colored based on the PANTHER
    \cite{Mi:2005qq} class of their primary target.}
  \label{fig:simnet}
\end{figure}
